---
title: "CA Weather"
author: "Yujun Zhou"
date: "May 2, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=30, fig.height=15) 

```

```{r,echo=FALSE}
library(ggplot2) #Calls: fortify, ggplot
library(rgdal)   
library(sp)      
library(raster)
library(gdalUtils)
library(parallel)
library(RCurl)
library(R.utils)
library(rgeos)
library(dplyr)
```
## 

Daily temperature (min and max) for each ward (1970/01/01- 2018/04/28)

```{r,echo=FALSE}
zmw_ward=readOGR("shapefiles/zmw/zwe_polbnda_adm3_250k_cso.shp")
```
```{r}
plot(zmw_ward)
```
## daily temperatures for each ward for the growing season (October to June) starting in October 2007 and ending in June 2011.
 
1. get ECMWF data (will need some python code to do the automatica download)
2. try with african drought monitor 




## 4 Rainfall Maps (CHIRPS daily rainfall data for the entire country, calculate cumulative seasonal rainfall )

a.       October 2007 – June 2008
b.       October 2008 – June 2009
c.       October 2009 – June 2010
d.       October 201 – June 2011

```{r,echo=FALSE}
library(readxl)
# CA_rain <- read_excel("shapefiles/zmw/CA_rain.xlsx", sheet = "Sheet1")
# 
# CA_rain2 <- read_excel("shapefiles/zmw/CA_rain.xlsx",sheet = "Sheet2")

```

create a “heat” map for cumulative season rainfall for all of Zimbabwe. 
He should be able to find a polygon layer for wards in Zimbabwe online. 

lay over the outlines of the surveyed wards on the “heat” map.


## 4 Temperature Maps (Gdd)



 