---
title: "CA Weather"
author: "Yujun Zhou"
date: "May 2, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=40, fig.height=40) 

```

```{r,include=FALSE}
library(ggplot2) #Calls: fortify, ggplot
library(rgdal)   
library(sp)      
library(raster)
library(gdalUtils)
library(parallel)
library(RCurl)
library(R.utils)
library(rgeos)
library(dplyr)
```


```{r,include=FALSE}
zmw_ward=readOGR("shapefiles/zmw/zwe_polbnda_adm3_250k_cso.shp")
```

```{r}
plot(zmw_ward)
```


## Daily temperature (min and max) for each ward (1970/01/01- 2018/04/28) 

Dataset extracted from African Drought Monitor (using extract_afm.R), see temp_min.csv and temp_max.csv 

```{r,include=FALSE}
# tmax0918 = read.csv("D:/zmw_daily_tmax09_18.csv")
# rlist <- list.files(path="D:/zmw_temp/tmax--GFS_ANALYSIS_BC", 
#                     pattern = "asc$",
#                     full.names=TRUE)
# #name_list<-gsub(pattern = "D:/zmw_temp/tmin--GFS_ANALYSIS_BC/",x=rlist,replacement = "")
# name_list<-gsub(pattern = "D:/zmw_temp/tmax--GFS_ANALYSIS_BC/",x=rlist,replacement = "")
# 
# #name_list<- gsub(pattern = "_GFS_ANALYSIS_BC_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "_GFS_ANALYSIS_BC_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "tmax",x=name_list,replacement = "")
# name_list<- gsub(pattern = "_daily.asc",x=name_list,replacement = "")
# 
# date1 = as.Date(name_list,"%Y%m%d")
# date1 = format(date1, "%m/%d/%Y")
# tmax0918$date1 = date1
```

```{r,include=FALSE}
# tmin0918 = read.csv("D:/zmw_daily_tmin09_18.csv")
# rlist <- list.files(path="D:/zmw_temp/tmin_GFS_ANALYSIS_BC", 
#                     pattern = "asc$",
#                     full.names=TRUE)
# #name_list<-gsub(pattern = "D:/zmw_temp/tmin--GFS_ANALYSIS_BC/",x=rlist,replacement = "")
# name_list<-gsub(pattern = "D:/zmw_temp/tmin_GFS_ANALYSIS_BC/",x=rlist,replacement = "")
# 
# #name_list<- gsub(pattern = "_GFS_ANALYSIS_BC_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "_GFS_ANALYSIS_BC_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "tmin",x=name_list,replacement = "")
# name_list<- gsub(pattern = "_daily.asc",x=name_list,replacement = "")
# 
# date1 = as.Date(name_list,"%Y%m%d")
# date1 = format(date1, "%m/%d/%Y")
# tmin0918$date1 = date1
```


```{r,include=FALSE}
# tmax7008 = read.csv("D:/zmw_daily_tmax70_08.csv")
# rlist <- list.files(path="D:/zmw_temp/tmax--PGF", 
#                     pattern = "asc$",
#                     full.names=TRUE)
# #name_list<-gsub(pattern = "D:/zmw_temp/tmin--GFS_ANALYSIS_BC/",x=rlist,replacement = "")
# name_list<-gsub(pattern = "D:/zmw_temp/tmax--PGF/",x=rlist,replacement = "")
# 
# #name_list<- gsub(pattern = "_GFS_ANALYSIS_BC_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "_PGF_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "tmax",x=name_list,replacement = "")
# name_list<- gsub(pattern = "_daily.asc",x=name_list,replacement = "")
# 
# date1 = as.Date(name_list,"%Y%m%d")
# date1 = format(date1, "%m/%d/%Y")
# tmax7008$date1 = date1
```

```{r,include=FALSE}
# 
# tmin7008 = read.csv("D:/zmw_daily_tmin70_08.csv")
# rlist <- list.files(path="D:/zmw_temp/tmin--PGF", 
#                     pattern = "asc$",
#                     full.names=TRUE)
# #name_list<-gsub(pattern = "D:/zmw_temp/tmin--GFS_ANALYSIS_BC/",x=rlist,replacement = "")
# name_list<-gsub(pattern = "D:/zmw_temp/tmin--PGF/",x=rlist,replacement = "")
# 
# #name_list<- gsub(pattern = "_GFS_ANALYSIS_BC_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "_PGF_",x=name_list,replacement = "")
# 
# name_list<- gsub(pattern = "tmin",x=name_list,replacement = "")
# name_list<- gsub(pattern = "_daily.asc",x=name_list,replacement = "")
# 
# date1 = as.Date(name_list,"%Y%m%d")
# date1 = format(date1, "%m/%d/%Y")
# tmin7008$date1 = date1

```


```{r,include=FALSE}
# 
# # combine different years 
# tmin_zmw = dplyr::bind_rows(tmin7008,tmin0918)
# tmax_zmw = dplyr::bind_rows(tmax7008,tmax0918)
# 
# # write them into csv file
# 
# write.csv(tmin_zmw, "D:/temp_min.csv")
# write.csv(tmax_zmw, "D:/temp_max.csv")

```

## Daily rainfall for each ward (1981/01/01- 2018/04/28) 

Dataset extracted from CHIRPS (using daily_rain_zmw.R), see daily_rain.csv   

```{r,include=FALSE}
# rain07 = read.csv("D:/zmw_daily_rain07.csv")
# rain07$date1= as.Date(rain07$date1,"%m/%d/%Y")
# 
# 
# rain0818 = read.csv("D:/zmw_daily_rain08_18.csv")
# raindate = read.csv("D:/datechirps.csv")
# rain0818$date1 = raindate$date1
# rain0818$date1= as.Date(rain0818$date1,"%m/%d/%Y")
# 
# 
# rain0718 = dplyr::bind_rows(rain07,rain0818)
# write.csv(rain0718,"D:/daily_rain.csv")

```

## Daily temperatures for each ward for the growing season (October to April) starting in October 2007 and ending in April 2011.

see growseason_temp_min.csv and growseason_temp_max.csv 


```{r,include=FALSE} 
# limit to the given time frame 
# 
tmax_zmw = read.csv("D:/temp_max.csv")
tmin_zmw = read.csv("D:/temp_min.csv")

tmin_zmw$Date= as.Date(tmin_zmw$Date,"%m/%d/%Y")
tmin0708 = tmin_zmw %>% dplyr::filter(Date>="2007-10-01" & Date<"2008-05-01")
tmin0809 = tmin_zmw %>% dplyr::filter(Date>="2008-10-01" & Date<"2009-05-01")
tmin0910 = tmin_zmw %>% dplyr::filter(Date>="2009-10-01" & Date<"2010-05-01")
tmin1011 = tmin_zmw %>% dplyr::filter(Date>="2010-10-01" & Date<"2011-05-01")


tmax_zmw$Date= as.Date(tmax_zmw$Date,"%m/%d/%Y")
tmax0708 = tmax_zmw %>% dplyr::filter(Date>="2007-10-01" & Date<"2008-05-01")
tmax0809 = tmax_zmw %>% dplyr::filter(Date>="2008-10-01" & Date<"2009-05-01")
tmax0910 = tmax_zmw %>% dplyr::filter(Date>="2009-10-01" & Date<"2010-05-01")
tmax1011 = tmax_zmw %>% dplyr::filter(Date>="2010-10-01" & Date<"2011-05-01")

growseason_temp_min = dplyr::bind_rows(tmin0708,tmin0809,tmin0910,tmin1011)
growseason_temp_max = dplyr::bind_rows(tmax0708,tmax0809,tmax0910,tmax1011)

# write.csv(growseason_temp_min,"D:/growseason_temp_min.csv")
# write.csv(growseason_temp_max,"D:/growseason_temp_max.csv")

```




## 4 Rainfall Maps (CHIRPS daily rainfall data for the entire country, calculate cumulative seasonal rainfall )

a.       October 2007 – April 2008
b.       October 2008 – April 2009
c.       October 2009 – April 2010
d.       October 2010 – April 2011


calculate total seasonal rainfall for each crop year
calculate mean seasonal rainfall for each crop year
calculate sd of rainfall for each crop year
Calculated z-score for each crop_year for each ward as absolute value of (total season rainfall – mean rainfall)/standard deviation

```{r,include=FALSE}
rain8107 = read.csv("D:/zmw_season_rain8107.csv")
rain8107$Date = as.Date(rain8107$Date,"%m/%d/%Y")
rain8107 = rain8107 %>% select(-yearmon)


rain8182 = rain8107 %>% dplyr::filter(Date>="1981-10-01" & Date<"1982-05-01") 
rain8283 = rain8107 %>% dplyr::filter(Date>="1982-10-01" & Date<"1983-05-01") 
rain8384 = rain8107 %>% dplyr::filter(Date>="1983-10-01" & Date<"1984-05-01") 
rain8485 = rain8107 %>% dplyr::filter(Date>="1984-10-01" & Date<"1985-05-01") 
rain8586 = rain8107 %>% dplyr::filter(Date>="1985-10-01" & Date<"1986-05-01") 
rain8687 = rain8107 %>% dplyr::filter(Date>="1986-10-01" & Date<"1987-05-01") 
rain8788 = rain8107 %>% dplyr::filter(Date>="1987-10-01" & Date<"1988-05-01") 
rain8889 = rain8107 %>% dplyr::filter(Date>="1988-10-01" & Date<"1989-05-01") 
rain8990 = rain8107 %>% dplyr::filter(Date>="1989-10-01" & Date<"1990-05-01") 
rain9091 = rain8107 %>% dplyr::filter(Date>="1990-10-01" & Date<"1991-05-01") 

rain9192 = rain8107 %>% dplyr::filter(Date>="1991-10-01" & Date<"1992-05-01") 
rain9293 = rain8107 %>% dplyr::filter(Date>="1992-10-01" & Date<"1993-05-01") 
rain9394 = rain8107 %>% dplyr::filter(Date>="1993-10-01" & Date<"1994-05-01") 
rain9495 = rain8107 %>% dplyr::filter(Date>="1994-10-01" & Date<"1995-05-01") 
rain9596 = rain8107 %>% dplyr::filter(Date>="1995-10-01" & Date<"1996-05-01") 
rain9697 = rain8107 %>% dplyr::filter(Date>="1996-10-01" & Date<"1997-05-01") 
rain9798 = rain8107 %>% dplyr::filter(Date>="1997-10-01" & Date<"1998-05-01") 
rain9899 = rain8107 %>% dplyr::filter(Date>="1998-10-01" & Date<"1999-05-01") 
rain9900 = rain8107 %>% dplyr::filter(Date>="1999-10-01" & Date<"2000-05-01") 
  
rain0001 = rain8107 %>% dplyr::filter(Date>="2000-10-01" & Date<"2001-05-01") 
rain0102 = rain8107 %>% dplyr::filter(Date>="2001-10-01" & Date<"2002-05-01") 
rain0203 = rain8107 %>% dplyr::filter(Date>="2002-10-01" & Date<"2003-05-01") 
rain0304 = rain8107 %>% dplyr::filter(Date>="2003-10-01" & Date<"2004-05-01") 
rain0405 = rain8107 %>% dplyr::filter(Date>="2004-10-01" & Date<"2005-05-01") 
rain0506 = rain8107 %>% dplyr::filter(Date>="2005-10-01" & Date<"2006-05-01") 
rain0607 = rain8107 %>% dplyr::filter(Date>="2006-10-01" & Date<"2007-05-01") 
 
rain0718 = read.csv("D:/daily_rain.csv")
rain0718$Date= as.Date(rain0718$Date,"%m/%d/%Y")
rain0708 = rain0718 %>% dplyr::filter(Date>="2007-10-01" & Date<"2008-05-01") 
rain0809 = rain0718 %>% dplyr::filter(Date>="2008-10-01" & Date<"2009-05-01") 
rain0910 = rain0718 %>% dplyr::filter(Date>="2009-10-01" & Date<"2010-05-01") 
rain1011 = rain0718 %>% dplyr::filter(Date>="2010-10-01" & Date<"2011-05-01") 

growseason_rain = dplyr::bind_rows(rain0708,rain0809,rain0910,rain1011)


write.csv(growseason_rain,"D:/growseason_rain.csv")

rainlist= list(rain8182,rain8283,rain8384,rain8485,rain8586,rain8687,rain8788,rain8889,rain8990,rain9091,rain9192,rain9293,rain9394,
rain9495,rain9596,rain9697,rain9798,rain9899,rain9900,rain0001,rain0102,rain0203,rain0304,rain0405,rain0506,rain0607,rain0708,rain0809,
rain0910,rain1011)

total_rain_list = lapply(rainlist,function(x){x %>% select(-Date) %>% colSums (na.rm = TRUE)})

totalrain_combine= total_rain_list[[1]]

for (i in 2:length(total_rain_list)){
  totalrain_combine = bind_rows(totalrain_combine,total_rain_list[[i]]) 
}

mean_rain = totalrain_combine %>% colMeans (na.rm = TRUE)

colSd <- function (x, na.rm=FALSE) apply(X=x, MARGIN=2, FUN=sd, na.rm=na.rm)
sd_rain = totalrain_combine %>% colSd (na.rm = TRUE)
z_score =   (totalrain_combine -mean_rain)/sd_rain

rain_year = read.csv("D:/rain_year.csv")
rain_year
z_score$rain_year = rain_year[,1]
totalrain_combine$rain_year = rain_year[,1]
z_score$rain_year

```

```{r,include=FALSE}

tmin8182 = tmin_zmw %>% dplyr::filter(Date>="1981-10-01" & Date<"1982-05-01") 
tmin8283 = tmin_zmw %>% dplyr::filter(Date>="1982-10-01" & Date<"1983-05-01") 
tmin8384 = tmin_zmw %>% dplyr::filter(Date>="1983-10-01" & Date<"1984-05-01") 
tmin8485 = tmin_zmw %>% dplyr::filter(Date>="1984-10-01" & Date<"1985-05-01") 
tmin8586 = tmin_zmw %>% dplyr::filter(Date>="1985-10-01" & Date<"1986-05-01") 
tmin8687 = tmin_zmw %>% dplyr::filter(Date>="1986-10-01" & Date<"1987-05-01") 
tmin8788 = tmin_zmw %>% dplyr::filter(Date>="1987-10-01" & Date<"1988-05-01") 
tmin8889 = tmin_zmw %>% dplyr::filter(Date>="1988-10-01" & Date<"1989-05-01") 
tmin8990 = tmin_zmw %>% dplyr::filter(Date>="1989-10-01" & Date<"1990-05-01") 
tmin9091 = tmin_zmw %>% dplyr::filter(Date>="1990-10-01" & Date<"1991-05-01") 

tmin9192 = tmin_zmw %>% dplyr::filter(Date>="1991-10-01" & Date<"1992-05-01") 
tmin9293 = tmin_zmw %>% dplyr::filter(Date>="1992-10-01" & Date<"1993-05-01") 
tmin9394 = tmin_zmw %>% dplyr::filter(Date>="1993-10-01" & Date<"1994-05-01") 
tmin9495 = tmin_zmw %>% dplyr::filter(Date>="1994-10-01" & Date<"1995-05-01") 
tmin9596 = tmin_zmw %>% dplyr::filter(Date>="1995-10-01" & Date<"1996-05-01") 
tmin9697 = tmin_zmw %>% dplyr::filter(Date>="1996-10-01" & Date<"1997-05-01") 
tmin9798 = tmin_zmw %>% dplyr::filter(Date>="1997-10-01" & Date<"1998-05-01") 
tmin9899 = tmin_zmw %>% dplyr::filter(Date>="1998-10-01" & Date<"1999-05-01") 
tmin9900 = tmin_zmw %>% dplyr::filter(Date>="1999-10-01" & Date<"2000-05-01") 

tmin0001 = tmin_zmw %>% dplyr::filter(Date>="2000-10-01" & Date<"2001-05-01") 
tmin0102 = tmin_zmw %>% dplyr::filter(Date>="2001-10-01" & Date<"2002-05-01") 
tmin0203 = tmin_zmw %>% dplyr::filter(Date>="2002-10-01" & Date<"2003-05-01") 
tmin0304 = tmin_zmw %>% dplyr::filter(Date>="2003-10-01" & Date<"2004-05-01") 
tmin0405 = tmin_zmw %>% dplyr::filter(Date>="2004-10-01" & Date<"2005-05-01") 
tmin0506 = tmin_zmw %>% dplyr::filter(Date>="2005-10-01" & Date<"2006-05-01") 
tmin0607 = tmin_zmw %>% dplyr::filter(Date>="2006-10-01" & Date<"2007-05-01") 

tmin0708 = tmin_zmw %>% dplyr::filter(Date>="2007-10-01" & Date<"2008-05-01") 
tmin0809 = tmin_zmw %>% dplyr::filter(Date>="2008-10-01" & Date<"2009-05-01") 
tmin0910 = tmin_zmw %>% dplyr::filter(Date>="2009-10-01" & Date<"2010-05-01") 
tmin1011 = tmin_zmw %>% dplyr::filter(Date>="2010-10-01" & Date<"2011-05-01") 

tmax8182 = tmax_zmw %>% dplyr::filter(Date>="1981-10-01" & Date<"1982-05-01") 
tmax8283 = tmax_zmw %>% dplyr::filter(Date>="1982-10-01" & Date<"1983-05-01") 
tmax8384 = tmax_zmw %>% dplyr::filter(Date>="1983-10-01" & Date<"1984-05-01") 
tmax8485 = tmax_zmw %>% dplyr::filter(Date>="1984-10-01" & Date<"1985-05-01") 
tmax8586 = tmax_zmw %>% dplyr::filter(Date>="1985-10-01" & Date<"1986-05-01") 
tmax8687 = tmax_zmw %>% dplyr::filter(Date>="1986-10-01" & Date<"1987-05-01") 
tmax8788 = tmax_zmw %>% dplyr::filter(Date>="1987-10-01" & Date<"1988-05-01") 
tmax8889 = tmax_zmw %>% dplyr::filter(Date>="1988-10-01" & Date<"1989-05-01") 
tmax8990 = tmax_zmw %>% dplyr::filter(Date>="1989-10-01" & Date<"1990-05-01") 
tmax9091 = tmax_zmw %>% dplyr::filter(Date>="1990-10-01" & Date<"1991-05-01") 

tmax9192 = tmax_zmw %>% dplyr::filter(Date>="1991-10-01" & Date<"1992-05-01") 
tmax9293 = tmax_zmw %>% dplyr::filter(Date>="1992-10-01" & Date<"1993-05-01") 
tmax9394 = tmax_zmw %>% dplyr::filter(Date>="1993-10-01" & Date<"1994-05-01") 
tmax9495 = tmax_zmw %>% dplyr::filter(Date>="1994-10-01" & Date<"1995-05-01") 
tmax9596 = tmax_zmw %>% dplyr::filter(Date>="1995-10-01" & Date<"1996-05-01") 
tmax9697 = tmax_zmw %>% dplyr::filter(Date>="1996-10-01" & Date<"1997-05-01") 
tmax9798 = tmax_zmw %>% dplyr::filter(Date>="1997-10-01" & Date<"1998-05-01") 
tmax9899 = tmax_zmw %>% dplyr::filter(Date>="1998-10-01" & Date<"1999-05-01") 
tmax9900 = tmax_zmw %>% dplyr::filter(Date>="1999-10-01" & Date<"2000-05-01") 

tmax0001 = tmax_zmw %>% dplyr::filter(Date>="2000-10-01" & Date<"2001-05-01") 
tmax0102 = tmax_zmw %>% dplyr::filter(Date>="2001-10-01" & Date<"2002-05-01") 
tmax0203 = tmax_zmw %>% dplyr::filter(Date>="2002-10-01" & Date<"2003-05-01") 
tmax0304 = tmax_zmw %>% dplyr::filter(Date>="2003-10-01" & Date<"2004-05-01") 
tmax0405 = tmax_zmw %>% dplyr::filter(Date>="2004-10-01" & Date<"2005-05-01") 
tmax0506 = tmax_zmw %>% dplyr::filter(Date>="2005-10-01" & Date<"2006-05-01") 
tmax0607 = tmax_zmw %>% dplyr::filter(Date>="2006-10-01" & Date<"2007-05-01") 

tmax0708 = tmax_zmw %>% dplyr::filter(Date>="2007-10-01" & Date<"2008-05-01") 
tmax0809 = tmax_zmw %>% dplyr::filter(Date>="2008-10-01" & Date<"2009-05-01") 
tmax0910 = tmax_zmw %>% dplyr::filter(Date>="2009-10-01" & Date<"2010-05-01") 
tmax1011 = tmax_zmw %>% dplyr::filter(Date>="2010-10-01" & Date<"2011-05-01") 


tminlist= list(tmin8182,tmin8283,tmin8384,tmin8485,tmin8586,tmin8687,tmin8788,tmin8889,tmin8990,tmin9091,tmin9192,tmin9293,tmin9394,
               tmin9495,tmin9596,tmin9697,tmin9798,tmin9899,tmin9900,tmin0001,tmin0102,tmin0203,tmin0304,tmin0405,tmin0506,tmin0607,tmin0708,tmin0809,
               tmin0910,tmin1011)

tmaxlist= list(tmax8182,tmax8283,tmax8384,tmax8485,tmax8586,tmax8687,tmax8788,tmax8889,tmax8990,tmax9091,tmax9192,tmax9293,tmax9394,
               tmax9495,tmax9596,tmax9697,tmax9798,tmax9899,tmax9900,tmax0001,tmax0102,tmax0203,tmax0304,tmax0405,tmax0506,tmax0607,tmax0708,tmax0809,
               tmax0910,tmax1011)

total_tmax_list = lapply(tmaxlist,function(x){x %>% select(-Date) %>% colMeans (na.rm = TRUE)})
total_tmin_list = lapply(tminlist,function(x){x %>% select(-Date) %>% colMeans (na.rm = TRUE)})


totaltmax_combine= total_tmax_list[[1]]
totaltmin_combine= total_tmin_list[[1]]


for (i in 2:length(total_tmax_list)){
  totaltmax_combine = bind_rows(totaltmax_combine,total_tmax_list[[i]]) 
}

for (i in 2:length(total_tmin_list)){
  totaltmin_combine = bind_rows(totaltmin_combine,total_tmin_list[[i]]) 
}

mean_temp_combine = (totaltmin_combine + totaltmin_combine)/2 - 273.15

mean_temp_mean = mean_temp_combine %>% colMeans (na.rm = TRUE)

colSd <- function (x, na.rm=FALSE) apply(X=x, MARGIN=2, FUN=sd, na.rm=na.rm)
sd_temp = mean_temp_combine %>% colSd (na.rm = TRUE)
z_score_temp =   (mean_temp_combine -mean_temp_mean)/sd_temp

rain_year = read.csv("D:/rain_year.csv")
temp_year = gsub(pattern = "rain",replacement ="temp",rain_year[,1])



z_score_temp$temp_year = temp_year
mean_temp_combine$temp_year = temp_year
```

```{r,include=FALSE}

tminlist= list(tmin8182,tmin8283,tmin8384,tmin8485,tmin8586,tmin8687,tmin8788,tmin8889,tmin8990,tmin9091,tmin9192,tmin9293,tmin9394,
               tmin9495,tmin9596,tmin9697,tmin9798,tmin9899,tmin9900,tmin0001,tmin0102,tmin0203,tmin0304,tmin0405,tmin0506,tmin0607,tmin0708,tmin0809,
               tmin0910,tmin1011)

tmaxlist= list(tmax8182,tmax8283,tmax8384,tmax8485,tmax8586,tmax8687,tmax8788,tmax8889,tmax8990,tmax9091,tmax9192,tmax9293,tmax9394,
               tmax9495,tmax9596,tmax9697,tmax9798,tmax9899,tmax9900,tmax0001,tmax0102,tmax0203,tmax0304,tmax0405,tmax0506,tmax0607,tmax0708,tmax0809,
               tmax0910,tmax1011)
tminlist_mean = lapply(tminlist,function(x){x %>% select(-Date) })
tmaxlist_mean = lapply(tmaxlist,function(x){x %>% select(-Date) })

tmeanlist = tminlist_mean

for (i in 1:length(tminlist_mean)){
tmeanlist[[i]] = (tminlist_mean[[i]] + tmaxlist_mean[[i]])/2- 273.15

}

date_list = lapply(tminlist,function(x){x %>% select(Date) })


for (i in 1:length(tmeanlist)){
tmeanlist[[i]] = cbind(date_list[[i]],tmeanlist[[i]])
}

tmeanlist[[1]]

gdd_list = lapply(tmeanlist,function(x){x %>% dplyr::mutate_all(funs(ifelse(.>8 & .<32,1,0))) %>% dplyr::summarise_all(funs(length(Date[.==1])))})

gdd_combine= gdd_list[[1]]

for (i in 2:length(gdd_list)){
  gdd_combine = bind_rows(gdd_combine,gdd_list[[i]]) 
}

gdd_combine$Date = 0
gdd_mean = gdd_combine %>% colMeans (na.rm = TRUE)

colSd <- function (x, na.rm=FALSE) apply(X=x, MARGIN=2, FUN=sd, na.rm=na.rm)
gdd_sd = gdd_combine %>% colSd (na.rm = TRUE)
gdd_z_score =   (gdd_combine -gdd_mean)/gdd_sd

gdd_combine$Date = temp_year
gdd_z_score$Date = temp_year
```

```{r,include=FALSE}
write.csv(gdd_combine,"D:/gdd_year.csv")
write.csv(gdd_z_score,"D:/gdd_z_score.csv")

write.csv(mean_temp_combine,"D:/mean_temp.csv")
write.csv(z_score_temp,"D:/temp_z_score.csv")



write.csv(totalrain_combine,"D:/total_rain.csv")
write.csv(z_score,"D:/rain_z_score.csv")

```

```{r,include=FALSE}
rain0708sum = rain0708 %>% select(-Date) %>% colSums (na.rm = TRUE)
rain0809sum = rain0809 %>% select(-Date) %>% colSums (na.rm = TRUE)
rain0910sum = rain0910 %>% select(-Date) %>% colSums (na.rm = TRUE)
rain1011sum = rain1011 %>% select(-Date) %>% colSums (na.rm = TRUE)


tmax0708sum = tmax0708 %>% select(-Date) %>% colMeans (na.rm = TRUE)
tmax0809sum = tmax0809 %>% select(-Date) %>% colMeans (na.rm = TRUE)
tmax0910sum = tmax0910 %>% select(-Date) %>% colMeans (na.rm = TRUE)
tmax1011sum = tmax1011 %>% select(-Date) %>% colMeans (na.rm = TRUE)

tmin0708sum = tmin0708 %>% select(-Date) %>% colMeans (na.rm = TRUE)
tmin0809sum = tmin0809 %>% select(-Date) %>% colMeans (na.rm = TRUE)
tmin0910sum = tmin0910 %>% select(-Date) %>% colMeans (na.rm = TRUE)
tmin1011sum = tmin1011 %>% select(-Date) %>% colMeans (na.rm = TRUE)

weather_list = list(tmax0708sum,tmax0809sum,tmax0910sum,tmax1011sum,tmin0708sum,tmin0809sum,tmin0910sum,tmin1011sum,rain0708sum,rain0809sum,rain0910sum,rain1011sum)

weather_list = lapply(weather_list,as.data.frame)
weather_list = lapply(weather_list,tibble::rownames_to_column)
colnames(weather_list[[1]]) = c("WARDPCODE","tmax0708")
colnames(weather_list[[2]]) = c("WARDPCODE","tmax0809")
colnames(weather_list[[3]]) = c("WARDPCODE","tmax0910")
colnames(weather_list[[4]]) = c("WARDPCODE","tmax1011")
colnames(weather_list[[5]]) = c("WARDPCODE","tmin0708")
colnames(weather_list[[6]]) = c("WARDPCODE","tmin0809")
colnames(weather_list[[7]]) = c("WARDPCODE","tmin0910")
colnames(weather_list[[8]]) = c("WARDPCODE","tmin1011")
colnames(weather_list[[9]]) = c("WARDPCODE","rain0708")
colnames(weather_list[[10]]) = c("WARDPCODE","rain0809")
colnames(weather_list[[11]]) = c("WARDPCODE","rain0910")
colnames(weather_list[[12]]) = c("WARDPCODE","rain1011")

map_data= dplyr::bind_cols(weather_list[[1]],weather_list[[2]][2])

for (i in 3:12){
  map_data = dplyr::bind_cols(map_data,weather_list[[i]][2])
  
}
map_data

map_data$tmax0708 = map_data$tmax0708-273.15
map_data$tmax0809 = map_data$tmax0809-273.15
map_data$tmax0910 = map_data$tmax0910-273.15
map_data$tmax1011 = map_data$tmax1011-273.15
map_data$tmin0708 = map_data$tmin0708-273.15
map_data$tmin0809 = map_data$tmin0809-273.15
map_data$tmin0910 = map_data$tmin0910-273.15
map_data$tmin1011 = map_data$tmin1011-273.15



map_data$tmean0708 <- rowMeans(map_data[c('tmax0708', 'tmin0708')], na.rm=TRUE)
map_data$tmean0809 = rowMeans(map_data[c('tmax0809', 'tmin0809')], na.rm=TRUE)
map_data$tmean0910 = rowMeans(map_data[c('tmax0910', 'tmin0910')], na.rm=TRUE)
map_data$tmean1011 = rowMeans(map_data[c('tmax1011', 'tmin1011')], na.rm=TRUE)

growseaon_mean0708 = (tmax0708 %>% select(-Date)+tmin0708 %>% select(-Date))/2 - 273.15
growseaon_mean0708$Date = tmax0708$Date
growseaon_mean0809 = (tmax0809 %>% select(-Date)+tmin0809 %>% select(-Date))/2 - 273.15
growseaon_mean0809$Date = tmax0809$Date
growseaon_mean0910 = (tmax0910 %>% select(-Date)+tmin0910 %>% select(-Date))/2 - 273.15
growseaon_mean0910$Date = tmax0910$Date
growseaon_mean1011 = (tmax1011 %>% select(-Date)+tmin1011 %>% select(-Date))/2 - 273.15
growseaon_mean1011$Date = tmax1011$Date



gdd_0708 = growseaon_mean0708 %>% 
          dplyr::mutate_all(funs(ifelse(.>8 & .<32,1,0))) %>%
          dplyr::summarise_all(funs(length(Date[.==1])))    
gdd_0809 = growseaon_mean0809 %>% 
  dplyr::mutate_all(funs(ifelse(.>8 & .<32,1,0))) %>%
  dplyr::summarise_all(funs(length(Date[.==1])))    
gdd_0910 = growseaon_mean0910 %>% 
  dplyr::mutate_all(funs(ifelse(.>8 & .<32,1,0))) %>%
  dplyr::summarise_all(funs(length(Date[.==1])))    
gdd_1011 = growseaon_mean1011 %>% 
  dplyr::mutate_all(funs(ifelse(.>8 & .<32,1,0))) %>%
  dplyr::summarise_all(funs(length(Date[.==1])))    

gdd= dplyr::bind_rows(gdd_0708,gdd_0809,gdd_0910,gdd_1011)
tgdd = t(gdd)
colnames(tgdd) =c("gdd_0708","gdd_0809","gdd_0910","gdd_1011")
tgdd = as.data.frame(tgdd) %>% tibble::rownames_to_column(var="WARDPCODE")
tgdd$WARDPCODE = gsub(pattern = "X",replacement = "",tgdd$WARDPCODE)
tgdd = tgdd %>% filter(WARDPCODE != "Date")

map_data = dplyr::bind_cols(map_data,tgdd)

write.csv(map_data,"D:/map_data.csv")
```

create a “heat” map for cumulative season rainfall, lay over the outlines of the surveyed wards on the “heat” map.


## 4 Temperature Maps (Gdd and mean temperature)

create a “heat” map for cumulative season rainfall, lay over the outlines of the surveyed wards on the “heat” map.




### check monthly rainfall data 

```{r,include=FALSE}
rain_check = read.csv("D:/month_rain_check2.csv")
#rain_check
Date = as.Date(rain_check$Date,"%m/%d/%Y")
#Date
library(zoo)
Month = as.yearmon(Date)
rain_check$year_mon = Month
check = rain_check %>% select(-Date)%>% group_by(year_mon) %>% dplyr::summarise_all(funs(sum))
check
write.csv(check,"D:/aggregated_rain_check2.csv")
#Month

```

 